Dynamic Walking and Whole-Body Motion Planning for Humanoid Robots: an Integrated Approach

### 2013-02-06 paper.tex
Update description of benchmark results extension.
Place extension description as first appendix and add ijrr url.
Mention extensions in figures.

\caption{HRP-2 grabs a ball on a shelf, puts it on another shelf, and comes back to 
  a rest position. Static balance constraints are enforced along the path, and 
  the intermediary goals consisting in grasping and displacing the ball are defined
  implicitly as inverse kinematics constraints.}
\label{fig:wb-shelves}
\end{figure}

@@

\caption{Horizontal trajectory of the robot CoM during
  locomotion. When the robot is close to obstacles, the amplitude of
  the oscillations decreases.}
\label{fig:chairs-waist}
\end{figure}

@@

\caption{Execution of the walking trajectory by HRP-2 on stage. The robot first goes
  to the shelves to release the ball, then comes back to a rest position.}

@@

\appendix
\section{Sliding Motion Planning Benchmarks}
\label{app:bench}

@@

\section{Index to Multimedia Extensions}

\begin{table}[H]
\begin{tabular}{c c m{0.7\linewidth}}
\hline
Extension & Type & Description \\
\hline
1 & Video & Example of a constrained motion planning result executed
on HRP-2. \\
2 & Video & Chairs scenario: solution of whole-body planning executed
on HRP-2. \\
3 & Video & Shelf scenario: solution of whole-body planning executed
in simulation and on HRP-2. \\
4 & Data & Raw data of sliding motion planning benchmarks for all
scenarios. \\
\hline
\end{tabular}
\end{table}

>>>>

\caption{HRP-2 grabs a ball on a shelf, puts it on another shelf, and
  comes back to a rest position. Static balance constraints are
  enforced along the path, and the intermediary goals consisting in
  grasping and displacing the ball are defined implicitly as inverse
  kinematics constraints. Extension 1 shows a video of the motion.}
\label{fig:wb-shelves}
\end{figure}

@@

\caption{Horizontal trajectory of the robot CoM during
  locomotion. When the robot is close to obstacles, the amplitude of
  the oscillations decreases. Extension 2 shows a video of the
  executed trajectory on the real HRP-2.}
\label{fig:chairs-waist}
\end{figure}

@@

\caption{Execution of the walking trajectory by HRP-2 on stage. The
  robot first goes to the shelves to release the ball, then comes back
  to a rest position. Extension 3 shows a video of this motion.}

@@

\appendix
\section{Index to Multimedia Extensions}

The multimedia extensions to this article are at:
\url{http://www.ijrr.org}.

\begin{table}[H]
\begin{tabular}{c c m{0.7\linewidth}}
\hline
Extension & Type & Description \\
\hline
1 & Video & Example of a constrained motion planning result executed
on HRP-2. \\
2 & Video & Chairs scenario: solution of whole-body planning executed
on HRP-2. \\
3 & Video & Shelf scenario: solution of whole-body planning executed
in simulation and on HRP-2. \\
4 & Data & Raw sliding motion planning benchmark results for Chairs,
Floating objects and Shelf Scenarios. \\
\hline
\end{tabular}
\end{table}

\section{Sliding Motion Planning Benchmarks}
\label{app:bench}

All plots were generated from data available in Extension 4.

@@
